Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-02-17 2017-EUROPAR/Gamification/paper.tex
Adding boilerplate

\section{Related Work}
\label{sec:experiments}
In volunteer distributed computing the BOINC projects applies a gamification technique 
by having a web page to present the ``Top 100 multi-project BOINC participants'' where
the name of the volunteer, the number of projects, GFLOPS, country and team are presented 
(\url{https://boinc.berkeley.edu/chart_list.php}).

@@

\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/puts_by_time.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}
\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/workers_best_user.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}
\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/workers_put_ip.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}

\bibliographystyle{abbrv}
\bibliography{../../bib/biblio,../../bib/evospace-i,../../bib/volunteer,../../bib/geneura}
\end{document}

>>>>

\section{Related Work}
\label{sec:soa}
In volunteer distributed computing the BOINC projects applies a gamification technique 
by having a web page to present the ``Top 100 multi-project BOINC participants'' where
the name of the volunteer, the number of projects, GFLOPS, country and team are presented 
(\url{https://boinc.berkeley.edu/chart_list.php}).

@@

\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/puts_by_time.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:om:puts}
  \end{figure*}
  %
\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/workers_best_user.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:om:workers}
\end{figure*}
\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/workers_put_ip.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:om:wp}
\end{figure*}

\section*{Acknowledgment}

This work has been supported in part by: de Ministerio espa\~{n}ol de
Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-3-P
(UGR-EPHEMECH).

\bibliographystyle{splncs03}
\bibliography{../../bib/biblio,../../bib/evospace-i,../../bib/volunteer,../../bib/geneura}
\end{document}
